HPC--101\\Onboarding

### 2016-06-23 hpc_101/paper.tex
rearranged slides regarding batch submission.  Updated globus endpoint names

\begin{frame}
	\frametitle{Globus}\footnotesize
\begin{block}{How do I get Globus?}
To utilize Globus, follow the following steps:
\begin{itemize}\tiny
\item Register for a Globus Online account -- \url{https://www.globusonline.org/signup}
\item Sign in to Globus Online (using your Globus Online username and password) -- \url{https://www.globusonline.org/signin}
\item Select ‘Start Transfer’ under ‘File Transfer’, or from the drop down menu in the top bar
\item You can view the list of available endpoints by clicking the button on the ‘Endpoint’ drop down box
\begin{itemize}\tiny
 \item Each of the login nodes is also an endpoint: \textbf{\emph{hawaii\#UHHPC1}} \& \textbf{\emph{hawaii\#UHHPC2}}
\end{itemize}
\item Once you select an endpoint, a login window will pop up. You can access the UHHPC endpoints by simply using your UH username and password. Enter your UH accounts username in the ‘Username’ field and UH accounts password in the ‘Password’ field and click ‘Authenticate’. 
\item You will see a listing of the contents of your home directory on the UH HPC. Double click on a directory to view its contents
\item Select a file or directory and click on the highlighted ‘arrow button’ to initiate the transfer
\end{itemize}
\end{block}
~\\
These instructions can also be found on the {\ci} website:~\\
{\footnotesize \href{http://www.hawaii.edu/its/ci/hpc-resources/hpc-tutorials/globus-quick-start-guide/}{http://www.hawaii.edu/its/ci/hpc-resources/hpc-tutorials/globus-quick-start-guide/}}
\end{frame}

@@

@@

\#!/bin/bash
\#SBATCH \ddash{}job-name=MPI\_example
\#SBATCH \ddash{}partition=exclusive.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=4
\#SBATCH \ddash{}tasks-per-node=20
\#SBATCH \ddash{}cpus-per-task=1
\#SBATCH \ddash{}error=hello-\%A.err \#\# \%A - filled with jobid
\#SBATCH \ddash{}output=hello-\%A.out \#\# \%A - filled with jobid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

\#!/bin/bash
\#SBATCH \ddash{}job-name=example
\#SBATCH \ddash{}partition=community.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\#SBATCH \ddash{}cpus-per-task=5
\#SBATCH \ddash{}mem=11000 \#\# max amount of memory per node you require
\#SBATCH \ddash{}error=hello-\%A.err \#\# \%A - filled with jobid
\#SBATCH \ddash{}output=hello-\%A.out \#\# \%A - filled with jobid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

@@

\#!/bin/bash
\#SBATCH \ddash{}job-name=example
\#SBATCH \ddash{}partition=community.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\#SBATCH \ddash{}cpus-per-task=5
\#SBATCH \ddash{}mem=11000 \#\# max amount of memory per node you require
\#SBATCH \ddash{}error=myprog-\%A\_\%a.err \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#SBATCH \ddash{}output=myprog-\%A\_\%a.out \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

\subsection{MPI Batch Job Example Script}
\begin{frame}[fragile]
\frametitle{SLURM sbatch -- Submission Script File -- GPU}
\begin{semiverbatim}\tiny
[login lus]\$ cat gpu.slurm

\#!/bin/bash
\#SBATCH \ddash{}job-name=GPU\_example
\#SBATCH \ddash{}partition=gpu.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\#SBATCH \ddash{}cpus-per-task=10
\#SBATCH \ddash{}gres=gpu:NV-K40:2  \#\# request both GPUs in the GPU node.
\#\#\# To request only 1 of the two GPUs in the node, you would do: gpu:NV-K40:1
\#SBATCH \ddash{}error=hello-\%A.err \#\# \%A - filled with jobid
\#SBATCH \ddash{}output=hello-\%A.out \#\# \%A - filled with jobid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

\subsection{Executing and Monitoring Batch Jobs}
\begin{frame}[fragile]
\frametitle{SLURM sbatch -- Executing \& Monitoring Jobs}\footnotesize
To execute a submission script you use the \textbf{\texttt{sbatch}} command
\begin{block}{Example -- Non Job Array}
\begin{semiverbatim}\tiny
[login lus]\$ sinfo
PARTITION     AVAIL  TIMELIMIT  NODES  STATE NODELIST
community.q   up     3-00:00:00 2      idle  compute-[0001-0002]
[login lus]\$ sbatch hello_world.slurm
sbatch: Submitted batch job 469
[login lus]\$ squeue
JOBID PARTITION    NAME     USER    ST TIME  NODES  NODELIST(REASON)
469   community.q  example  user99  R  00:01 1      compute-0001
\end{semiverbatim}
\end{block}
\begin{block}{Example -- Job Array}
\begin{semiverbatim}\tiny
[login lus]\$ sinfo
PARTITION     AVAIL  TIMELIMIT  NODES  STATE NODELIST
community.q   up     3-00:00:00 2      idle  compute-[0001-0002]
[login lus]\$ sbatch {\ddash}array=1-30 job_array.slurm
sbatch: Submitted batch job 470
[login lus]\$ squeue
JOBID      PARTITION    NAME     USER    ST   TIME    NODES  NODELIST(REASON)
470[1-30]  community.q  example  user99  PD   00:00   1      (resource)
470_1      community.q  example  user99  R    00:01   1      compute-0001
470_2      community.q  example  user99  R    00:05   1      compute-0002
\end{semiverbatim}
\end{block}

\begin{frame}
  \frametitle{Slurm Job Array}
  \includegraphics[width=1\textwidth]{images/job_array}

>>>>

\begin{frame}
	\frametitle{Globus}\footnotesize
\begin{block}{How do I get Globus?}
To utilize Globus, follow the following steps:
\begin{itemize}\tiny
\item Register for a Globus Online account -- \url{https://www.globusonline.org/signup}
\item Sign in to Globus Online (using your Globus Online username and password) -- \url{https://www.globusonline.org/signin}
\item Select ‘Start Transfer’ under ‘File Transfer’, or from the drop down menu in the top bar
\item You can view the list of available endpoints by clicking the button on the ‘Endpoint’ drop down box
\begin{itemize}\tiny
 \item Each of the login nodes is also an endpoint: \textbf{\emph{UHHPC1}} \& \textbf{\emph{UHHPC2}}
\end{itemize}
\item Once you select an endpoint, a login window will pop up. You can access the UHHPC endpoints by simply using your UH username and password. Enter your UH accounts username in the ‘Username’ field and UH accounts password in the ‘Password’ field and click ‘Authenticate’. 
\item You will see a listing of the contents of your home directory on the UH HPC. Double click on a directory to view its contents
\item Select a file or directory and click on the highlighted ‘arrow button’ to initiate the transfer
\end{itemize}
\end{block}
~\\
These instructions can also be found on the {\ci} website:~\\
{\footnotesize \href{http://www.hawaii.edu/its/ci/hpc-resources/hpc-tutorials/globus-quick-start-guide/}{http://www.hawaii.edu/its/ci/hpc-resources/hpc-tutorials/globus-quick-start-guide/}}
\end{frame}

@@

\subsection{GPU Batch Job Example Script}
\begin{frame}[fragile]
\frametitle{SLURM sbatch -- Submission Script File -- GPU}
\begin{semiverbatim}\tiny
[login lus]\$ cat gpu.slurm

\#!/bin/bash
\#SBATCH \ddash{}job-name=GPU\_example
\textcolor{blue}{\#SBATCH \ddash{}partition=gpu.q}
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\textcolor{blue}{\#SBATCH \ddash{}cpus-per-task=10}
\textcolor{blue}{\#SBATCH \ddash{}mem=11000} \#\# max amount of memory per node you require
\textcolor{blue}{\#SBATCH \ddash{}gres=gpu:NV-K40:2 } \#\# request both GPUs in the GPU node.
\#\#\# To request only 1 of the two GPUs in the node, you would do: gpu:NV-K40:1
\#SBATCH \ddash{}error=hello-\%A.err \#\# \%A - filled with jobid
\#SBATCH \ddash{}output=hello-\%A.out \#\# \%A - filled with jobid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

\#!/bin/bash
\#SBATCH \ddash{}job-name=MPI\_example
\textcolor{blue}{\#SBATCH \ddash{}partition=exclusive.q}
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\textcolor{blue}{\#SBATCH \ddash{}nodes=4}
\textcolor{blue}{\#SBATCH \ddash{}tasks-per-node=20}
\textcolor{blue}{\#SBATCH \ddash{}cpus-per-task=1}
\#SBATCH \ddash{}error=hello-\%A.err \#\# \%A - filled with jobid
\#SBATCH \ddash{}output=hello-\%A.out \#\# \%A - filled with jobid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

\#!/bin/bash
\#SBATCH \ddash{}job-name=example
\textcolor{blue}{\#SBATCH \ddash{}partition=community.q}
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\textcolor{blue}{\#SBATCH \ddash{}cpus-per-task=5}
\textcolor{blue}{\#SBATCH \ddash{}mem=11000} \#\# max amount of memory per node you require
\#SBATCH \ddash{}error=hello-\%A.err \#\# \%A - filled with jobid
\#SBATCH \ddash{}output=hello-\%A.out \#\# \%A - filled with jobid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

\subsection{Executing and Monitoring Batch Jobs}
\begin{frame}[fragile]
\frametitle{SLURM sbatch -- Executing \& Monitoring Jobs}\footnotesize
To execute a submission script you use the \textbf{\texttt{sbatch}} command
\begin{block}{Example}
\begin{semiverbatim}\tiny
[login lus]\$ sinfo
PARTITION     AVAIL  TIMELIMIT  NODES  STATE NODELIST
community.q   up     3-00:00:00 2      idle  compute-[0001-0002]

[login lus]\$ sbatch hello_world.slurm
sbatch: Submitted batch job 469

[login lus]\$ squeue
JOBID PARTITION    NAME     USER    ST TIME  NODES  NODELIST(REASON)
469   community.q  example  user99  R  00:01 1      compute-0001
\end{semiverbatim}
\end{block}

\btVFill
\begin{center}What if I want to run many jobs with identical parameters, but on different inputs?~\\
  SLURM provides a mechanism for this called a \textbf{Job Array}.\end{center}

\begin{frame}
  \frametitle{Slurm Job Array}
\begin{center}  
  \includegraphics[width=0.90\textwidth]{images/job_array}
\end{center}
\end{frame}

@@

\#!/bin/bash
\#SBATCH \ddash{}job-name=example
\#SBATCH \ddash{}partition=community.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\#SBATCH \ddash{}cpus-per-task=5
\#SBATCH \ddash{}mem=11000 \#\# max amount of memory per node you require
\textcolor{blue}{\#SBATCH \ddash{}error=myprog-\%A\_\%a.err} \#\# \%A - filled with jobid. \%a - filled with job arrayid
\textcolor{blue}{\#SBATCH \ddash{}output=myprog-\%A\_\%a.out} \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

\subsection{Executing and Monitoring Job Array Batch Jobs}

\begin{frame}[fragile]
\frametitle{SLURM sbatch -- Executing \& Monitoring Job Arrays}\footnotesize
\begin{block}{Example}
\begin{semiverbatim}\tiny
[login lus]\$ sinfo
PARTITION     AVAIL  TIMELIMIT  NODES  STATE NODELIST
community.q   up     3-00:00:00 2      idle  compute-[0001-0002]

[login lus]\$ sbatch {\ddash}array=1-30 job_array.slurm
sbatch: Submitted batch job 470

[login lus]\$ squeue
JOBID      PARTITION    NAME     USER    ST   TIME    NODES  NODELIST(REASON)
470[1-30]  community.q  example  user99  PD   00:00   1      (resource)
470_1      community.q  example  user99  R    00:01   1      compute-0001
470_2      community.q  example  user99  R    00:05   1      compute-0002
\end{semiverbatim}
\end{block}
\end{frame}
